---
title: "demo"
author: "kun"
date: "9/3/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # global config
```

## r code
```{r echo=FALSE}
x = 5
```

inline data `r x`, math on it `r pi * x^2`.

```{r cars, echo=TRUE}
summary(cars)
```

## plot

```{r pressure, tidy=TRUE, echo=FALSE}
plot(pressure)
```

```{r out.width='.49\\linewidth', fig.width=3, fig.height=3, fig.show='hold', fig.align='center', echo=FALSE}
par(mar = c(4, 4, 0.2, 0.1))
plot(cars, pch = 19)
plot(pressure, pch = 17)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(grid)
library(gridExtra)
p1 <- ggplot(mtcars) + aes(x = hp, y = mpg) + geom_point()
p2 <- ggplot(mtcars) + aes(x = factor(cyl), y = mpg) + geom_boxplot() +
    geom_smooth(aes(group = 1), se = FALSE)
grid.arrange(p1, p2, ncol = 2)
```


## plain
End a line with two spaces  
to start a new paragraph.

*italics* and **bold**

`verbatim code`

sub/superscript^2^~2~

~~strikethrough~~

escaped: \* \_ \\

endash: --, emdash: ---

## table
| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
| 12 | 12 | 12 | 12 |
| 123 | 123 | 123 | 123 |
| 1 | 1 | 1 | 1 |

## math
inline LaTeX equations $f(k) = {n \choose k} p^{k} (1-p)^{n-k}$ within single dollar

equation block: $$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$$

$$\begin{array}{ccc}
x_{11} & x_{12} & x_{13}\\
x_{21} & x_{22} & x_{23}
\end{array}$$

$$X = \begin{bmatrix}1 & x_{1}\\
1 & x_{2}\\
1 & x_{3}
\end{bmatrix}$$

$$\Theta = \begin{pmatrix}\alpha & \beta\\
\gamma & \delta
\end{pmatrix}$$

$$\begin{vmatrix}a & b\\
c & d
\end{vmatrix}=ad-bc$$

## unordered list
- one item
- one item
    - one more item
    - one more item

## ordered list
1. the first item
2. the second item
    - one more item
    - one more item

## blockquote
> "I thoroughly disapprove of duels. If a man should challenge me,
  I would take him kindly and forgivingly by the hand and lead him
  to a quiet place and kill him."
>
> --- Mark Twain
